\section{Summary and Reflection}
{\tiny Written by: Kandaker Majharul Islam}\\

The Inventory Management System presented in this report offers a streamlined solution for locker rentals within educational institutions, enhancing convenience for users and administrators alike. Rooted in the core values of Sustainability, Equality, and Stress-less, the project aims to create an inclusive and eco-friendly system.

\subsection{Core Functionality}

The system's core functionality encompasses renting devices and lockers, managing their allocations, and providing reporting tools. Users can easily rent lockers and devices, while administrators oversee allocations and address reported issues promptly.

\subsection{Team Composition}

The project's success owes much to the diverse skills and collaboration among team members. Teams were structured to optimize expertise and ensure comprehensive development, with clear responsibilities outlined for each member.

\subsection{Reflection and Lessons Learned}

Reflecting on the project, several factors contributed to its success, including effective communication, positive team dynamics, and the utilization of Kanban boards for task management. Notable lessons learned include the importance of investing in quality components, considering alternative hosting platforms, and initiating testing earlier in the development cycle.

\subsubsection{Successes}

Effective communication, positive team dynamics, and skill integration through pair programming were key successes contributing to the project's outcome.

\subsubsection{Areas for Improvement}

Identified areas for improvement include investing in quality components, considering hosting platforms, consolidating API documentation, and initiating testing earlier in the development cycle.

\subsection{Acknowledgments}
In conclusion, the project taught us a lot and gave us valuable experiences to learn from. We're thankful to Professors Anne Keskitalo from Centria University and Bettina Harriehausen-Mühlbauer from Hochschule Darmstadt for letting us explore a new place, learn new things, and work with people from different countries. We really enjoyed this experience and are grateful for the opportunity.
