\section{Motivation}
{\tiny Written by: Jingya Zhao}\\

This project was inspired by a presentation on a equipment database, which addressed functionalities for adding equipment data, searching the database, and managing equipment borrowing and returns. The presentation highlighted the importance of some features:
\begin{itemize}
    \item Tracking equipment details (owner, purchase date, location)
    \item Searching equipment by type, brand, and location
    \item Reserving equipment
    \item Reporting equipment issues
\end{itemize}

These functionalities match perfectly with the challenges faced by universities in managing tech equipment. Universities typically rely on manual processes, leading to limited access for students, difficulties managing device charging, and a burden on IT staff for equipment tracking and maintenance.

We saw an opportunity to utilise the principles underlying equipment databases. This led us to develop a locker system that could address these limitations. The locker system would provide:
\begin{itemize}
    \item Easy access for students: Allowing them to reserve and pick up equipment through a user-friendly interface.
    \item Uninterrupted use for professors: Offering dedicated lockers for charging personal devices.
    \item Efficient management for IT administrators: Providing an automated system for booking and device tracking, eliminating manual processes.
\end{itemize}

To ensure a smooth experience for all users, we decided to design four key functions for the locker system:

\begin{enumerate}
    \item \textbf{Device Rental}: Users can browse and reserve equipment through a user-friendly website. Once reserved, a unique code is provided for locker access. This same code allows them to retrieve the equipment and return it. Users can easily report any broken or malfunctioning equipment directly through the website.
    \item \textbf{Device Charging}: Lockers can be used to conveniently charge personal devices. The system displays real-time power consumption information, allowing users to monitor their device's charging status.
    \item \textbf{IT Admin Management}: IT administrators can efficiently manage all devices and bookings within the system. This includes adding new equipment, tracking reservations, and overseeing overall system operations.
    \item \textbf{Equipment Issue Reporting}: Users can easily report any broken or malfunctioning equipment directly through the website. This ensures prompt maintenance and helps maintain the quality and availability of the equipment.
\end{enumerate}

By creating this university locker system, we aimed to improve accessibility, convenience, and overall equipment management for the university community.
